Component response rate variation underlies the stability of complex systems

### 2020-03-15 notebook/SI.Rmd
Remove the correlation effects on stability from the SI, as these are now in the main text

- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Structured network construction](#structured)
- [Feasibility of complex systems](#Feasibility)
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Consistency with Gibbs et al. (2018)](#Gibbs)
- [Effects of matrix correlations](#rhos)

@@

Effects of matrix correlations
================================================================================

>>>>

- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Stability of structured networks](#structured)
- [Feasibility of complex systems](#Feasibility)
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Consistency with Gibbs et al. (2018)](#Gibbs)

@@
